%% Copyright 2020 All Rights Reserved
%% SPDX-License-Identifier: GNU General Public License v2.0 only
%% This program is free software; you can redistribute it and/or modify it under the terms of the GNU General Public License as published by the Free Software Foundation; version 2.

%% This program is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details.

%% You should have received a copy of the GNU General Public License along with this program; if not, write to the Free Software Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston

\chapter{Reference}\label{sec:something}

    \begin{algorithm}
    \caption{Discounted Interest Rate}\label{euclid}
    \hspace*{\algorithmicindent} \textbf{Input} \\
    \hspace*{\algorithmicindent} \textbf{Output} 
    \begin{algorithmic}[1]
    \Procedure{MyProcedure}{}
%    \Procedure{MyProcedure}{$x,y$}
%     % Input:
%     \Comment{Input: x}
%     % Output:
%     \Comment{Output:y}
    \State $\textit{stringlen} \gets \textit{length of } \textit{string}$
    \State $i \gets \textit{patlen}$
    \BState \emph{top}:
    \If {$i > \textit{stringlen}$} \Return false
    \EndIf
    \State $j \gets \textit{patlen}$
    \BState \emph{loop}:
    \If {$\textit{string}(i) = \textit{path}(j)$}
    \State $j \gets j-1$.
    \State $i \gets i-1$.
    \State \textbf{goto} \emph{loop}.
    \State \textbf{close};
    \EndIf
    \State $i \gets i+\max(\textit{delta}_1(\textit{string}(i)),\textit{delta}_2(j))$.
    \State \textbf{goto} \emph{top}.
    \EndProcedure
    \end{algorithmic}
    \end{algorithm}

 \cleardoublepage

\chapter{Sources}

\section{Informative}


\newline
\text{
The Pricing of Forward Ship Value Agreements and the Unbiasedness of
Implied Forward Prices in the Second-Hand Market for Ships. Maritime
Economics and Logistics (2004). Link}
\newline

\text{A.; Whinston Mas-Colell. Equilibrium and its Basic Welfare
Properties. Microeconomic Theory Oxford University Press, 2010.}
\newline

\text{EconPapers: Pricing of forwards and other derivatives in
cointegrated commodity markets. In Energy Economics. (2015).}
\newline

\section{References}
\text{Wood, G.: Ethereum yellow paper (2014)}
\newline

\text{Perez, D., Livshits, B.: Broken metre: Attacking resource
metering in evm. arXiv preprint arXiv:1909.07220}
\newline

\text{Zero-intelligence realized variance estimation, Jim Gatheral and Roel C.A. Oomen}
\newline

OPCODE and read/write performance 
\newline

\text{Lien Finance: Derivative Stable Coin -An auction based maturity
derivative for  an algorithmic stablecoin design}
\newline

\text{ETH 2.0 Sharding and I/O performance, netting balances approach
has higher read costs.}
\newline

\text{Dune Analytics Documentation}

\text{EIP-1559 discussed by Vitalik }
 \cleardoublepage
 
 \begin{thebibliography}{9}
\bibitem{latexcompanion} 

\bibitem{Smart Contract Analysis Tools} 
Ghaleb, Asem and Pattabiraman, Karthik
[\textit{How Effective Are Smart Contract Analysis Tools? Evaluating Smart Contract Static Analysis Tools Using Bug Injection}],
Proceedings of the 29th ACM SIGSOFT International Symposium on Software Testing and Analysis
\text{2020}

 
\bibitem{Solidity Verify} 
Hajdu, Akos and Jovanovi,  Dejan
\textit{solc-verify: A Modular Verifier for {S}olidity Smart Contracts},
\text{2020},
    booktitle  = {Verified Software. Theories, Tools, and Experiments},
    series     = {Lecture Notes in Computer Science},
    volume     = {12301},
\text{Springer},
\text{Chakraborty, Supratik and Navas, Jorge A.},
\text{161-179},
text{ISBN: 978-3-030-41600-3},
\text{10.1007/978-3-030-41600-3_11},


\bibitem{GFI Swaps Exchange} 
\texttt{GFI Swaps Exchange LLC },
\textit{GFI. 2015. GFI Swaps Exchange LLC rulebook. GFI Technical Report.
\text{2015},
    },
\footnote{https://www.cftc.gov/sites/default/files/stellent/groups/public/otherif/
documents/ifdocs/exhibitm1rulebookgfiswaps.pdf},

\bibitem{Myersonian Approach to Dynamic Mechanism Design} 
   
\texttt{Pavan, A I. Segal, and J. Toikka.},
\textit{Dynamic mechanism design: A Myersonian approach.},
\text{2014},
\text{ 82:601–53.},
\text{Econometrica},


\bibitem{Stochastic Integration and Differential Equations} 
Protter. P.
\textit{Stochastic integration and diﬀerential equations. second edition.},
\text{2005.},
    publisher  ={Heidelberg: Springer.},


\bibitem{Price Inference in Small Markets} 
Rostek., M.. and M., Weretka.
\textit{ Price inference in small markets: Dynamic thin markets.},
\text{2012. 80:687–711. 2015.},
\text{Econometrica },
\text{  Review of Financial Studies 28:2946–92.},


\bibitem{Dark Pools impact on Price Discovery} 
@incollection{
        
\textttYe. L.},
\textit{ Understanding the impacts of dark pools on price discovery},
\text{2016},
\text{The Chinese University of Hong Kong. Shenzhen.},
\text{https://arxiv.org/pdf/1612.08486.pdf},


\bibitem{Liquidity Based Model of Security Design} 
@incollection{
    
\texttt"Peter DeMarzo"},
\textit{"A Liquidity Based Model of Security Design"},
\text{1999},
    publisher  ={Econometrica},
\text{Volume 67: 65-99.},

    
    \footnote{The copyright to this article is held by the Econometric Society. http://www.econometricsociety.org.},

\bibitem{Optimal Innovation of Futures Contracts} 
@incollection{
\texttt"Matthew O. Jackson"},
\textit{"Optimal Innovation of Futures Contracts"},
\text{1989},
    series     = { Review of Financial Studies},
\text{Volume 2: 275-296},


\end{thebibliography}

