%% Copyright 2020 All Rights Reserved
%% SPDX-License-Identifier: GNU General Public License v2.0 only
%% 
%%  This program is free software; you can redistribute it and/or modify it
%%  under the terms of the GNU General Public License as published by the Free
%%  Software Foundation; version 2.
%% 
%%  This program is distributed in the hope that it will be useful, but WITHOUT
%%  ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS
%%  FOR A PARTICULAR PURPOSE. See the GNU General Public License for more details.
%%  You should have received a copy of the GNU General Public License along
%%  with this program; if not, write to the Free Software Foundation, Inc., 51
%%  Franklin Street, Fifth Floor, Boston



%% EVO %% 
%% EVO %% 

\chapter{Introduction}\label{sec:introduction}

EVO Protocol presents an idea of embedded volumetric optionality, which in essence is a mechanism for controllable
liquidity through the mechanism of volume. Any 
asset would be "less" accelerating in price swings depending on the chose parameters. One consequence is that
significant volume movements, such as "rug pulls" or 
legitimate price action movements, incur a cost onto the liquidating party. This, in essence, ensures orderly market
liquidation to a degree with an additional 
benefit of helping provide an orderly unwinding / unwinding period for instruments utilizing the protocol. Instruments
may produce predictable inflation rates, 
enabling them to be lent out through other protocols, furthering market stabilizing effects. Such token can be a
reasonable investment choice purposed for the 
"storage of value".

\section{Abstract}\label{sec:preamble}
A Generalized Protocol Specification for Volumetric Manifolds and a reference implementation. Features include an
embedded 
volumetric mechanism to enforce desired behaviors
based upon robust economic incentives.\footnote{An analogy to help understand these terms is the
\textbf{ManifoldSystem}. The \textbf{ManifoldEpoch} is equivalent to the Epoch,
the \textbf{ManifoldVolume} is equivalent to the
transfer rate, and the \textbf{ManifoldFee} is the
Fee for the Transfer Rate.}

%\lstset{language=TeX,numbers=none}
%\begin{lstlisting}[frame=lines]
\begin{verbatim}
Key Concepts: Automatic Stabilizers, embedded volumetric
optionality, liquidity, transaction unwinding, 
transaction execution, price stability, self stability
 \end{verbatim}
%\end{lstlisting}
    \vspace{2mm}

\subsection{Transaction Unwinding: Risk and Execution and Settlement}

How does selling against an order book work? How do you measure risk of not being able to liquidate your position? Any
trader (esp. low volume
low liquidity) can tell you how a tin order book will make it 
impossible to profit on a trade. We can look at Almgren's Optimal 
Execution of Portfolio Transactions\footnote{Almgren 1998, https://www.math.nyu.edu/faculty/chriss/optliq_f.pdf} on
their analysis of the situation:
    \vspace{2mm}
\subsection{Trade Half Life}
This analysis yields a number we call the "half-life" of a trade, the 
natural time for execution in the absence of exogenous time 
constraints. For example, in trading a highly illiquid, volatile 
security, there are two extreme strategies: trade everything now at a 
known, but high cost, or trade in equal sized packets over $x$ time 
at a relatively lower cost. The latter strategy has lower expected cost but this comes at the expense of greater
uncertainty in total revenue.
    \vspace{2mm}
\subsection{Optimal Execution of Portfolio Transactions}
    \vspace{2mm}
\subsection{Front Running and Backrunning}
This can be expressed as the common "Gas Wars" events of network 
congestion on ethereum foundation, or sending in a transaction knowingly under priced in the expectation it will be
included in a block in $x$ amount of time from now. Basically discounting a future 
block inclusion as an acceptable cost versus having it included relatively sooner (i.e. you would rather spend less get
it later than 
spend more and have it now).

$Twait$\text{discounted future block inclusion }
    \vspace{2mm}
$Twait$\text{ discounted future block inclusion}
    \vspace{2mm}
$$Tunwind$$ time to liquidate position



We can define this as what we call the time it takes to unwind a position (i.e. liquidation period)

    \vspace{2mm}

All we can do is insist that for a given level uncertainty, cost be minimized.We can say that trade execution is the
"Dynamic trading
strategy that provides the minimum expected cost of trading over $x$
period of time"\footnote{Almgren 1998}. As such we can say that the
strategy employed for transaction pricing in the first auction system
can be that of expectations of future physical settlement (i.e.
transaction being included in the block) versus willingness to pay for
that inclusion (i.e bidding expressed in transaction fees).
    \vspace{2mm}
\subsection{Volumetric Contracting}

A Volumetric futures contract would be buying a contract for a certain
volume of goods, such as freight space, gas (i.e. natural gas
products), or $block space$. Block space as a tradable volumetric
futures contract could be achieved by creating a set of contracts in
which gas token can either be re-packaged, re-sold (auction), or burned and minted.
    \vspace{2mm}
\subsection{Establishing Parameters for Transfer Rate}

\begin{tabular}{llrr}
\hline Strategy & Parameter & Gas price & Blocks waited \\
\hline Geth & \(S =1.0\) & 4,414,902,746 & 1.97 \\
Geth & \(S =0.9\) & 4,080,968,868 & 15.49 \\
Geth & \(S =0.8\) & 3,531,922,197 & 25.52 \\
\hline Look-ahead & \(B =15\) & 1,166,965,099 & 4.80 \\
Look-ahead & \(B =30\) & 969,559,938 & 8.52 \\
Look-ahead & \(B =60\) & 782,105,012 & 18.84 \\
\hline Proposed approach & \(U =1.0\) & 2,120,108,703 & 3.28 \\
Proposed approach & \(U =0.9\) & 1,908,097,833 & 3.79 \\
Proposed approach & \(U =0.8\) & 1,696,086,963 & 5.13 \\
Proposed approach & \(U =0.7\) & 1,484,076,092 & 10.06
\end{tabular}
    \vspace{2mm}
\subsection{Contract Delivery and Contract Rollover Dates}
    \vspace{2mm}
We can extrapolate the contract for date of delivery as being subsets of $B$ and be able to 
approximate ideal delivery time for contracts. To the extent of future pricing concerns could 
express themselves beyond 30 days is  likely unrealistic at this stage. 
    \vspace{2mm}
This preliminary model is used in deciding the parameters for the first market on \textbf{evo 
protocol}, gasevo, which is $24 days$
    \vspace{2mm}
In the paper Blockchain Resource Pricing \footnote{page 14 of
https://github.com/ethereum/research/raw/master/papers/pricing/ethpricing.pdf p43)} Buterin
illustrates that how under, "full block conditions, cryptocurrency price fluctuation is lower than
transaction fee fluctuations". By denominating things as "fixed fees" which utilize a unit of
account denominated in cryptocurrency, it actually leads to more (fiat-denominated) price
predictability than a market with bidding and a gas limit. In essence this is a "cap and trade" regime of monetary
policy. 
    \vspace{2mm}

\subsection{Ethereum as a Cap and Trade Regime}
The regression finds that, after accounting for this social uncle rate, one byte accounts for an
additional ~0.000002 uncle rate. Bytes in a transaction take up 68 gas, of which 61 gas accounts
for its contribution to bandwidth (the remaining 7 is for bloating the history database). If we
want the bandwidth coefficient and the computation coefficient in the gas table to both reflect
propagation time, then this implies that if we wanted to really optimize gas costs, we would need
to increase the gas cost per byte by 50 (ie. to 138). This would also entail raising the base gas
cost of a transaction by 5500 (note: such a re balance would not mean that everything gets more
expensive; the gas limit would be raised by ~10% so that the average-case transaction throughput
would remain unchanged). 
\quote{Vitalik Buterin, ethermagican forums}

\vspace{2mm}
\footnote{ One relatively simple way to implement this is that ½ of the tx fee goes to the miner
who mined the tx, and the other ½ goes into the "spread-out tx fee bucket". Each time a block is
mined, 1% of the ZEC in the "spread-out tx fee bucket" goes to the miner who mined that block.
}

\section{A Fiction of Value}
'Fictitious Capital' is the price of a non-produced resource like land. Since the ownership of the
land entails a stream of rent payments in the future, the capitalized value of these prospective
rent payments can generate a market price of the plot of land.  The common modern conception of the functions of money
includes a store of value, unit of account and a medium of exchange.

It is common to consider functions of money as a medium of exchange, store of value and unit of 
account. In this work we highlight yet another function of money, namely as a unit of contract 
execution. Historically, there has always been an implicit paper contract behind money. However, 
with the rise of cryptocurrencies, we now have 'programmable money', where it is easy to bind 
digital assets to an explicit contract. We use the term contractual money to refer to digital 
money with a usage contract in the form of executable code.

An example of 'fictitious capital' is the price of a non-produced resource like land.
Since ownership of the land entails a stream of rent payments in the future, the capitalized value
of these prospective rent payments can generate a market price of the plot of land. For the owner 
of the plot of land, the price of the plot of land functions like capital, generating a stream of 
profit-like


\footnote{The paradox for the labour theory of value that there are items in capitalism which command a 
price but have no value, i.e., have zero embodied socially necessary abstract labour.}

\footnote{Our forthcoming stack, Maidenlane, is a  dematerialization protocol for contractual agreements, i.e  a unit of
contract 
execution. The physicality of documentary trade is replaced by a new paradigm of electronic 
scarcity, expressed normally through a distributed blockchain protocol.  }
